### 2023-07-14 2.State/lstm.tex
lstm fixes

\acp{LSTM} come in reality in a few different flavor. Usually, when \acp{LSTM} are mentionned, the version used is the \ac{NP} version. This is the most common version as those are the equations described on the wikipedia page \cite{wikiLSTM} and used in librairies like Keras \cite{Keras} or pyTorch. In fact is that there are total of 8 other variations of \acp{LSTM} \cite{nbLSTM}.
The difference between each of them varies from one to the other, but they can all be described with new equations.

@@

\begin{equation}\label{eq:inputGVanilla}
  i_t=\sigma (w_i\cdot[x_{t_1},h_{t-1}] + b_i+c_{t-1}\odot p_f)
\end{equation}
\begin{equation}\label{eq:forgetGVanilla}
  f_t=\sigma (w_f\cdot[x_{t_1},h_{t-1}] + b_f+c_{t-1}\odot p_i)
\end{equation}
\begin{equation}\label{eq:ouputGVanilla}
  o_t=\sigma (w_o\cdot[x_{t_1},h_{t-1}] + b_o+c_{t}\odot p_o)
\end{equation}
With $p_f$, $p_i$ and $p_o$ being the peephole weights vectors. Their size is the same as the size of the hidden state vector ($h_t$).

>>>>

\acp{LSTM} come in reality in a few different flavor. Usually, when \acp{LSTM} are mentionned, the version used is the \ac{NP} version. This is the most common version as those are the equations described on the wikipedia page \cite{wikiLSTM} and used in librairies like Keras \cite{Keras} or pyTorch \cite{PyTorch}. In fact is that there are total of 8 other variations of \acp{LSTM} \cite{nbLSTM}.
The difference between each of them varies from one to the other, but they can all be described with new equations.

@@

\begin{equation}\label{eq:inputGVanilla}
  i_t=\sigma (w_i\cdot[x_{t_1},h_{t-1}] + b_i+c_{t-1}\odot p_f)
\end{equation}
\begin{equation}\label{eq:forgetGVanilla}
  f_t=\sigma (w_f\cdot[x_{t_1},h_{t-1}] + b_f+c_{t-1}\odot p_i)
\end{equation}
\begin{equation}\label{eq:ouputGVanilla}
  o_t=\sigma (w_o\cdot[x_{t_1},h_{t-1}] + b_o+c_{t}\odot p_o)
\end{equation}
With $p_f$, $p_i$ and $p_o$ being the peephole weights vectors. Their size is the same as the size of the hidden state vector ($h_t$). $\odot$ is the pointwise multiplication operator.
